\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-17 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: using listings package in a separate document
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59755 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

\begin{center}
 \includegraphics[width=0.48\textwidth]{svg_images/grass6-topo}
 \hspace{10mm}
 \includegraphics[width=0.48\textwidth]{svg_images/grass7-topo}
 \newline
 Figure 1b: Topology changes from version 6 to 7 after [5]
\end{center}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{PyGRASS: fast Python API}{
[Zambelli 2013]

>>> from grass.pygrass.vector.geometry import Point, Line

>>> point = Point()
>>> point.x = 150.65
>>> point.y = 368.50
>>> point
>>> Point(150.650000, 368.500000)
>>> point.distance(Point(160.2, 372.6))
10.39290623454286
%%%%>>> point.get_wkt()
'POINT(150.650000 368.500000)'

>>> line = Line([(5, 12), (6, 13), (4, 19)])
>>> line.bbox()
Bbox(19.0, 12.0, 6.0, 4.0)

>>>>

\usepackage{listings}

@@

\begin{center}
 \includegraphics[width=0.48\textwidth]{svg_images/grass6-topo}
 \hspace{10mm}
 \includegraphics[width=0.48\textwidth]{svg_images/grass7-topo}
 \newline
 Figure 1b: Topology changes from version 6 to 7 after [Landa 2013]
\end{center}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{PyGRASS: fast Python API}{
PyGRASS [Zambelli 2013] is an object-oriented Python API which allows efficient manipulation with vectors.
It is easy-to-use but its performance is comparable to C code since it calls GRASS C API behind the scenes.

\includegraphics[width=0.9\textwidth]{texpdfs/pygrass_code}
